Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: significant improvement in the dark energy figure of merit

### 2017-09-27 Draft/Draft1.1.tex
minor changes

%\documentclass[preprint,prd,aps,amsmath,amssymb,nofootinbib]{revtex4}
%\documentclass[prd,aps,amsmath,amssymb,nofootinbib]{revtex4}
%\documentclass[aps,twocolumn,showpacs,floatfix,superscriptaddress]{revtex4}
\documentclass[prl,twocolumn,superscriptaddress,aps,amsmath,amssymb,nofootinbib,altaffilletter]{revtex4}
%\documentclass[prl,superscriptaddress,twocolumn,nopreprintnumbers,floatfix,preprintnumbers,altaffilletter]{revtex4}

\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{array}
\usepackage{multirow}
\usepackage{float}
\usepackage{color}
\graphicspath{{figs/}}

@@

@@

\author{ 
Xiao-Dong Li,$^{1}$
Cristiano G. Sabiu,$^{2}$
Changbom Park,$^{1}$
Yuting Wang,$^{3}$
Gong-bo Zhao,$^{3}$
Hyunbae Park,$^{2}$
Arman Shafieloo,$^{2}$
Juhan Kim,$^{4}$
and Sungwook E. Hong$^{2}$}

  \affiliation{School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 02455, Korea}
  \affiliation{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
  \affiliation{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
  \affiliation{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 02455, Korea}

\begin{abstract}
We use the anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
allowing for competitive and unbiased constrains to be placed on cosmological parameters.
We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, yield
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results 
reduces the error bars by $\sim$30-40\%,
%and reduces the area of $w_0-w_a$ contour by 50\%.
and improves the dark energy figure of merit by a factor of 2. 
The AP method can %be combined with the standard BAO method,
greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

\pacs{95.36.+x, 98.80.–k}
\maketitle

@@

%\section{Introduction}
{\it Introduction.}---
The  origin  of  the late-time accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
Theoretical explanations for this phenomena are many and range from a non-zero  vacuum energy and evolving  scalar  fields  remnant  from  the  big  bang, 
to modifications of Einstein's General Relativity\cite{2012IJMPD..2130002Y}. 
Considering the wealth of theoretical explanations, 
it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
differentiate between competing models.

@@

In this paper, we continue to develop our previous methodology and proceed to infer the constraints on dynamical dark energy. 
We will present a slightly improved methodology to that of our previous work\citep{Li2016}, 
allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces. 
The methodology we will present here, can be applied to any model of dynamical dark energy, 
or indeed any appropriately chosen parametric or non-parametric decomposition of the cosmic expansion history. 
However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization\cite{CPL_CP,CPL_L},
\begin{equation}
w(z) = w_0 + w_a (1-a) = w_0 + w_a \frac{z}{1+z}.
\end{equation}
This parametrization characterizes dark energy equation-of-state (EoS) by two free parameters.
$w_0$ determines the present-day value, while parameter $w_a$ characterizes the first-order derivative of $w$ with respect to $a$.

@@

%\section{Methodology}\label{sec:method}
{\it Methodology.}---

The spectroscopic galaxy sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
the LOWZ sample, designed as an extension of the SDSS-I/II luminous red galaxy sample to $z\approx 0.4$ and fainter luminosities,
and the CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$),
targeted to be an approximately stellar mass limited sample of massive, luminous galaxies \cite{Reidetal:2016}.
In the clustering analysis we use 1,133,326 galaxies, split into six, non-overlapping redshift bins, 
$0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
The number density of galaxies and the redshift binning scheme is plotted in the left panel of Fig.\ref{fig_TpCF}.

@@

In detail, the number of pairs are only counted in a fiducial cosmology
-- which is taken as the $\Omega_m=0.26$ $\Lambda$CDM --
and ``translated'' to the measurements in a ``target'' cosmology using the relations, 
\begin{eqnarray}
 s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}^2+\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}, \\
 \mu_{\rm target} = \mu_{\rm fiducial} \frac{\alpha_\parallel}
 {\sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}^2 +\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}}
\end{eqnarray}
where $\alpha_{\bot}\equiv D_{A,\rm target}/D_{A,\rm fiducial}$,
$\alpha_{\parallel}\equiv H_{\rm fiducial}/H_{\rm target}$.
and values of $D_A$ and $H$ are computed in the effective redshifts of the six redshift bins.
In the fiducial cosmology
we measure $\xi(s,\mu)$ with a high resolution of
$\Delta s = 0.2 {\rm Mpc/h}$, $\Delta \mu = 1/600$,
%Let us call this ``approximate 2pCF'' method.
%to obtain the accurate number counts 
and these small ``pixels'' are grouped to infer 
the number counts in other cosmologies, 
in large pixels of $\Delta s = 1 {\rm Mpc/h}$, $\Delta \mu = 1/120$.
%in the fiducial cosmology and group the bins in the target cosmology.
In the case when one small pixel belongs to more than one larger pixel,
a correction is applied by computing the fraction of the overlapping area.

We found when using the approximate method the computed 
$\hat\xi_{\Delta s}(\mu)$ in a non-fiducial cosmology suffers from
an error of $\lesssim0.5\%$, which is 10 times smaller than the statistical noise.
We checked that the approximate method can reproduce the results presented in \cite{Li2016} quite well.

@@

%\section{Results}\label{sec:results}
{\it Results.}---

@@

The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% 
and reduces the $w_0-w_a$ (95.4\% CL) contour by 50\%.
This constitutes a significant increase in the figure of merit constraints on $(w_0, w_a)$. 
This doubling of the figure of merit comes at no additional cost or alteration to data size, 
thus greatly improving the overall cost-benefit consideration of large cosmological redshift surveys.

@@

%\section{Conclusion}\label{sec:conclusion}
{\it Conclusion.}---

In recent studies we have proposed to constrain cosmological parameters 
governing the expansion history of the universe via 
the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
This approach enables a robust AP test on relatively small scales.
In this paper we improved the methodology and obtained a tight constraint 
on the CPL parametrization of dark energy.
%using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
%12 spanning the redshift range $0.15<z<0.69$ . 
%Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.

@@

@@

\begin{acknowledgments}
We thank Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
CGS acknowledges support from the National Research Foundation (NRF,  \#2017R1D1A1B03034900). 
We thank Stephen Appleby, Seokcheon Lee, Maurice van Putten, Graziano Rossi and Yi Wang for helpful discussions.

Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the
National Science Foundation, and the U.S. Department of Energy Office of Science. 
The SDSS-III web site is http://www.sdss3.org/. 
SDSS-III is managed by the Astrophysical Research Consortium for the Participating Institutions
of the SDSS-III Collaboration.
\end{acknowledgments}

%% After the acknowledgments section, use the following syntax and the
%% \facility{} macro to list the keywords of facilities used in the research
%% for the paper.  Each keyword will be checked against the master list during
%% copy editing.  Individual instruments or configurations can be provided
%% in parentheses, after the keyword, but they will not be verified.

%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc.

%% The reference list follows the main body and any appendices.
%% Use LaTeX's thebibliography environment to mark up your reference list.
%% Note \begin{thebibliography} is followed by an empty set of
%% curly braces.  If you forget this, LaTeX will generate the error
%% "Perhaps a missing \item?".
%%
%% thebibliography produces citations in the text using \bibitem-\cite
%% cross-referencing. Each reference is preceded by a
%% \bibitem command that defines in curly braces the KEY that corresponds
%% to the KEY in the \cite commands (see the first section above).
%% Make sure that you provide a unique KEY for every \bibitem or else the
%% paper will not LaTeX. The square brackets should contain
%% the citation text that LaTeX will insert in
%% place of the \cite commands.

%% We have used macros to produce journal name abbreviations.
%% AASTeX provides a number of these for the more frequently-cited journals.
%% See the Author Guide for a list of them.

%% Note that the style of the \bibitem labels (in []) is slightly
%% different from previous examples.  The natbib system solves a host
%% of citation expression problems, but it is necessary to clearly
%% delimit the year from the author name used in the citation.
%% See the natbib documentation for more details and options.

%\bibitem[Canizares et al.(1978)]{can78} Canizares, C. R.,
%    Grindlay, J. E., Hiltner, W. A., Liller, W., \&
%    McClintock, J. E.  1978, \apj, 224, 39

%Wang Q H, Lindon O, Hardle W. 
%Semiparametric regression analysis with missing response at random. 
%J Am Stat Assoc, 2004, 99: 334－345

\begin{thebibliography}{}
%\citep{Riess:1998}
%[astro-ph/0205436].
\bibitem{Li2016}%[Li et al.(2016)]
Li, X.-D., Park, C., \& Sabiu, C.G., et al. 2016, ApJ, 832, 103

>>>>

%%% On-going present
%%
%% Beginning of file 'sample.tex'
%%
%% Modified 2005 December 5
%%
%% This is a sample manuscript marked up using the
%% AASTeX v5.x LaTeX 2e macros.

%% The first piece of markup in an AASTeX v5.x document
%% is the \documentclass command. LaTeX will ignore
%% any data that comes before this command.

%% The command below calls the preprint style  
%% which will produce a one-column, single-spaced document.
%% Examples of commands for other substyles follow. Use
%% whichever is most appropriate for your purposes.
%%
%%\documentclass[12pt,preprint]{aastex}

%% manuscript produces a one-column, double-spaced document:

%%\documentclass[manuscript]{aastex}

%% preprint2 produces a double-column, single-spaced document:

 %\documentclass[preprint2]{aastex}
%\documentclass[preprint2]{aastex}
%\documentclass[manuscript]{aastex}
\documentclass[iop]{emulateapj}
\renewcommand{\baselinestretch}{0.95}
%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

%% \documentclass[preprint2,longabstract]{aastex}

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
%% If you are submitting to a journal that translates manuscripts
%% into SGML, you need to follow certain guidelines when preparing
%% your macros. See the AASTeX v5.x Author Guide
%% for information.

\usepackage{enumitem}

\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$~}\fi}} 
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

%% You can insert a short comment on the title page using the command below.

%\slugcomment{Not to appear in Nonlearned J., 45.}

%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%% The left head contains a list of authors,
%% usually a maximum of three (otherwise use et al.).  The right
%% head is a modified title of up to roughly 44 characters.
%% Running heads will not print in the manuscript style.

%\title[]
%{}

\shorttitle{Significantly improved dark energy figure of merit from reshift dependence of AP effect}
\shortauthors{X.-D. Li, C. Park, C.G. Sabiu, H. Park, D.H. Weinberg, J. Kim, S.E. Hong}

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

@@

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire.

@@

%\author{Xiao-Dong~Li\altaffilmark{1}, Changbom~Park\altaffilmark{1}, J.~E.~Forero-Romero\altaffilmark{2} and Juhan Kim%\altaffilmark{3}}
%\affil{\altaffilmark{1}School of Physics, Korea Institute for Advanced Study, Heogiro 85, Seoul 130-722, Korea }
%\affil{\altaffilmark{2}Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, %Colombia}
%\affil{\altaffilmark{3}Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-%gu, Seoul 130-722, Korea }
%\affil{\it (xiaodongli@kias.re.kr, cbp@kias.re.kr, je.forero@uniandes.edu.co, kjhan@kias.re.kr)}

%\author[Xiao-Dong~Li, Changbom~Park, Cristiano G. Sabiu, Juhan Kim and Sungwook E. Hong]
%{ Xiao-Dong Li$^{1,\dagger}$, Changbom Park$^{1}$, Cristiano G. Sabiu$^{2}$, Juhan Kim$^{3,1,\star}$, Sungwook E. Hong$^{1}$\\
%$^1$School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea\\
%$^2$Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea\\
%$^3$Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea\\
%$^{\dagger}$xiaodongli@kias.re.kr\\
%$\star$Corresponding Author: ***@kasi.re.kr}

\author{Xiao-Dong Li,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cristiano G. Sabiu,}
\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
\author{Changbom Park,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Yuting Wang, Gong-bo Zhao}
\affil{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
\author{Hyunbae Park, Arman Shafieloo,}
\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
\author{Juhan Kim,}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 02455, Korea}
\author{and Sungwook E. Hong}
\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}

%\altaffiltext{1}{xiaodongli@kias.re.kr}
%\altaffiltext{2}{cbp@kias.re.kr}
%\altaffiltext{3}{csabiu@kasi.re.kr}
%\altaffiltext{4}{\bf Hyunbae: your email}
\altaffiltext{1}{Corresponding Author: kjhan@kias.re.kr}

% \email{xiaodongli@kias.re.kr}
% \email{cbp@kias.re.kr}
% \email{je.forero@uniandes.edu.co}

% \author{S. Djorgovski\altaffilmark{1,2,3} and Ivan R. King\altaffilmark{1}}
% \affil{Astronomy Department, University of California,
%     Berkeley, CA 94720}
%
% \author{C. D. Biemesderfer\altaffilmark{4,5}}
% \affil{National Optical Astronomy Observatories, Tucson, AZ 85719}
% \email{aastex-help@aas.org}
%
% \and
%
% \author{R. J. Hanisch\altaffilmark{5}}
% \affil{Space Telescope Science Institute, Baltimore, MD 21218}
%
% %% Notice that each of these authors has alternate affiliations, which
% %% are identified by the \altaffilmark after each name.  Specify alternate
% %% affiliation information with \altaffiltext, with one command per each
% %% affiliation.
%
% \altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
% CTIO is operated by AURA, Inc.\ under contract to the National Science
% Foundation.}
% \altaffiltext{2}{Society of Fellows, Harvard University.}
% \altaffiltext{3}{present address: Center for Astrophysics,
%     60 Garden Street, Cambridge, MA 02138}
% \altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
% \altaffiltext{5}{Patron, Alonso's Bar and Grill}

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

\begin{abstract}
We use the anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016},
we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
allowing for competitive and unbiased constrains to be placed on cosmological parameters.
% The Alcock-Paczynski (AP) test was performed via the redshift dependence of clustering on scales of 6-40 $h^{-1}\rm Mpc$.
% We improve the methodology of \citep{Li2016} by significantly reducing its computation time, 
% which enables us to explore three or more cosmological parameters.
% We applied the improved method on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$.
We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, yield
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results 
reduces the error bars by $\sim$30-40\%,
%and reduces the area of $w_0-w_a$ contour by 50\%.
and improves the dark energy figure of merit by a factor of 2. 
% We carefully checked the robustness of the results.
The AP method can %be combined with the standard BAO method,
greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

%% Keywords should appear after the \end{abstract} command. The uncommented
%% example has been keyed in ApJ style. See the instructions to authors
%% for the journal to which you are submitting your paper to determine
%% what keyword punctuation is appropriate.

\keywords{large-scale structure of Universe --- dark energy --- cosmological parameters}

%% From the front matter, we move on to the body of the paper.
%% In the first two sections, notice the use of the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below. We have
%% chosen the first three characters of the first author's name plus
%% the last two numeral of the year of publication as our KEY for
%% each reference.

%% Authors who wish to have the most important objects in their paper
%% linked in the electronic edition to a data center may do so by tagging
%% their objects with \objectname{} or \object{}.  Each macro takes the
%% object name as its required argument. The optional, square-bracket
%% argument should be used in cases where the data center identification
%% differs from what is to be printed in the paper.  The text appearing
%% in curly braces is what will appear in print in the published paper.
%% If the object name is recognized by the data centers, it will be linked
%% in the electronic edition to the object data available at the data centers
%%
%% Note that for sources with brackets in their names, e.g. [WEG2004] 14h-090,
%% the brackets must be escaped with backslashes when used in the first
%% square-bracket argument, for instance, \object[\[WEG2004\] 14h-090]{90}).
%%  Otherwise, LaTeX will issue an error.

\section{Introduction}

@@

The  origin  of  the late-time accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
Theoretical explanations for this phenomena are many and range from a non-zero  vacuum energy and evolving  scalar  fields  remnant  from  the  big  bang, 
to modifications of Einstein's General Relativity\cite{2012IJMPD..2130002Y}. 
Considering the wealth of theoretical explanations, 
it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
differentiate between competing models.

@@

In this paper, we continue to develop our previous methodology and proceed to infer the constraints on dynamical dark energy. 
We will present a slightly improved methodology to that of our previous work\citep{Li2016}, 
allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces. 
The methodology we will present here, can be applied to any model of dynamical dark energy, 
or indeed any appropriately chosen parametric or non-parametric decomposition of the cosmic expansion history. 
However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization\cite{CPL_CP,CPL_L},
\begin{equation}
w(z) = w_0 + w_a (1-a) = w_0 + w_a \frac{z}{1+z}.
\end{equation}
This parametrization characterizes dark energy equation-of-state (EoS) by two free parameters.
$w_0$ determines the present-day value, while parameter $w_a$ characterizes the first-order derivative of $w$ with respect to $a$. 
The possible redshift evolution of dark energy EoS is not considered in the analysis of \cite{Li2016}.

@@

%{\bf AMTB: Please chose one kind of tense of verbs. It changes from sentences to sentences!}
%{\bf AMTB: How many mock BOSS samples are made from HR4?}

\section{Methodology}
The spectroscopic galaxy sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
the LOWZ sample, designed as an extension of the SDSS-I/II luminous red galaxy sample to $z\approx 0.4$ and fainter luminosities,
and the CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$),
targeted to be an approximately stellar mass limited sample of massive, luminous galaxies \cite{Reidetal:2016}.
In the clustering analysis we use 1,133,326 galaxies, split into six, non-overlapping redshift bins, 
$0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
The number density of galaxies and the redshift binning scheme is plotted in the left panel of Fig.\ref{fig_TpCF}.

@@

In detail, the number of pairs are only counted in a fiducial cosmology
-- which is taken as the $\Omega_m=0.26$ $\Lambda$CDM --
and ``translated'' to the measurements in a ``target'' cosmology using the relations, 
\begin{eqnarray}\label{eq:smumap}
 s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}^2+\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}, \\
 \mu_{\rm target} = \mu_{\rm fiducial} \frac{\alpha_\parallel}
 {\sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}^2 +\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}}
\end{eqnarray}
where $\alpha_{\bot}\equiv D_{A,\rm target}/D_{A,\rm fiducial}$,
$\alpha_{\parallel}\equiv H_{\rm fiducial}/H_{\rm target}$.
and values of $D_A$ and $H$ are computed in the effective redshifts of the six redshift bins.
%The left panel of Figure \ref{fig_method} shows how 
%$\xi(s,\mu)$ is mapped from the fiducial cosmology to another cosmology using the above relations.
In the fiducial cosmology
we measure $\xi(s,\mu)$ with a high resolution of
$\Delta s = 0.2 {\rm Mpc/h}$, $\Delta \mu = 1/600$,
%Let us call this ``approximate 2pCF'' method.
%to obtain the accurate number counts 
and these small ``pixels'' are grouped to infer 
the number counts in other cosmologies, 
in large pixels of $\Delta s = 1 {\rm Mpc/h}$, $\Delta \mu = 1/120$.
%in the fiducial cosmology and group the bins in the target cosmology.
In the case when one small pixel belongs to more than one larger pixel,
a correction is applied by computing the fraction of the overlapping area.
%\footnote{A dense grid can effectively reduce the ``edge effect'' produced when we map $\xi(s,\mu)$ from one cosmology to another.
%The edge effect would introduce artificial correlations between nearby pixels, smooth $\xi(s,\mu)$ a little bit, 
%reduce the value of $\chi^2$, and change the obtained cosmological constriants.
%We found that, using $\Delta s = 1 {\rm Mpc/h}$ and $\Delta \mu = 1/120$, 
%the cosmological constraints of \cite{Li2016} can not be properly reproduced.}.

We found when using the approximate method the computed 
$\hat\xi_{\Delta s}(\mu)$ in a non-fiducial cosmology suffers from
an error of $\lesssim0.5\%$, which is 10 times smaller than the statistical noise.
We checked that the approximate method can reproduce the results presented in \cite{Li2016} quite well.
% We checked that the approximate method can reproduce the results of precise method quite well.
% The right panel of Figure \cite{fig_method} shows the  $\Omega_m$-$w_0$ constraints obtained 
%  using the precise and approximate 2pCFs (here we fix $w_a=0$). 
%  They agree with each other quite well.

%\begin{figure*}
%   \centering{
%   \includegraphics[width=6cm]{fig_smu.eps}
%   \includegraphics[width=10.5cm]{fig_comp.eps}
%   }
%   \caption{\label{fig_method}
%   Left panel: Mapping $\xi(s,\mu)$ from the fiducial cosmology to four other cosmologies. 
% The number counts are measured in the fiducial cosmology in a uniform grid (blue dashed.
%  Just for illustration; the grid adopted in real analysis is much denser).
% In the four cosmologies with $(\Omega_m,w) = (0.31,-1.5),\ (0.31,-0.5),\ (0.41,-1.0)\ \rm and\ (0.21,-1.0)$, 
% %due to the distortion of geometry,
% the distribution of number counts in $(s, \mu)$ space becomes the red solid grid ({\bf Check}).
% We utilize the mapping realtion to approximate the 2pCF in vaiours cosmologies, without re-conducting the 2pCF statistics. 
% Right panel: Cosmological constraints in the $\Omega_m$-$w_0$ plane, with the value of $w_a$ fixed as zero.
% Results obtained using the precise 2pCFs (gray filled) 
% and approximate 2pCFs (blue solid) 2pCFs matches each other quite well.
%   }
%\end{figure*}

%

@@

\section{Result}

@@

The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
%\cite{Li2016} 
Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% 
and reduces the $w_0-w_a$ (95.4\% CL) contour by 50\%.
This constitutes a significant increase in the figure of merit constraints on $(w_0, w_a)$. 
This doubling of the figure of merit comes at no additional cost or alteration to data size, 
thus greatly improving the overall cost-benefit consideration of large cosmological redshift surveys.

@@

%\section{Conclusion}\label{sec:conclusion}
\section{Conclusion}

In recent studies we have proposed to constrain cosmological parameters 
governing the expansion history of the universe via 
the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
This approach enables a robust AP test on relatively small scales.
In this paper we improved the methodology and obtained a tight constraint 
on the CPL parametrization of dark energy.
%The derived cosmological constraints are fully consistent with a cosmological constant 
%dark energy component having no redshift evolution.

%using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
%12 spanning the redshift range $0.15<z<0.69$ . 
%Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.

@@

\section*{Acknowledgments}

We thank Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
CGS acknowledges support from the National Research Foundation (NRF,  \#2017R1D1A1B03034900). 
We thank Stephen Appleby, Seokcheon Lee, Maurice van Putten, Graziano Rossi and Yi Wang for helpful discussions.

Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the
National Science Foundation, and the U.S. Department of Energy Office of Science. 
The SDSS-III web site is http://www.sdss3.org/. 
SDSS-III is managed by the Astrophysical Research Consortium for the Participating Institutions
of the SDSS-III Collaboration including the University of Arizona, the Brazilian Participation Group, Brookhaven
National Laboratory, Carnegie Mellon University, University of Florida, the French Participation Group, 
the German Participation Group, Harvard University, the Instituto de Astrofisica de Canarias, the Michigan State/Notre
Dame/JINA Participation Group, Johns Hopkins University, Lawrence Berkeley National Laboratory, Max Planck
Institute for Astrophysics, Max Planck Institute for Extraterrestrial Physics, New Mexico State University, New
York University, Ohio State University, Pennsylvania State
University, University of Portsmouth, Princeton University,
the Spanish Participation Group, University of Tokyo, University of Utah, Vanderbilt University, University of Virginia, 
University of Washington, and Yale University.

@@

\begin{thebibliography}{}

\bibitem[Ade et al. (2015)]{Planck2015}
Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589

\bibitem[Alam et al.(2016)]{Alam2016}
Alam, S., Ata, M., \& Bailey, S., et al. 2016,
submitted to MNRAS (arXiv:1607.03155)

\bibitem[Albrecht et al.(2006)]{DETF}
Albrecht, A., Bernstein, G., \& Cahn, R., et al. 2006. [astro-ph/0609591].

%\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
%  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
%  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
%{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12

\bibitem[Alcock \& Paczynski(1979)]{AP1979}
Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358

%\bibitem[Anderson et al.(2012)]{2012MNRAS.427.3435A} 
%Anderson, L., Aubourg, E., Bailey, S., et al.\ 2012, MNRAS, 427, 3435

\bibitem[Anderson et al.(2013)]{Anderson2013}
Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24

%\bibitem[Bassett et al.(2002)]{Bassett2002}
%Bassett, B.A., Kunz, M., Silk, J., \& Ungarelli, C. 2002, MNRAS, 336, 1217

\bibitem[Ballinger, Peacock \& Heavens 1996]{Ballinger1996}
Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877

\bibitem[Betoule et al.(2014)]{JLA}
Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32

\bibitem[Beutler et al.(2011)]{6dFGS}
Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017

%\bibitem[Beutler et al.(2013)]{Beutler2013}
%Beutler, F., Saito, S., \& Seo, H.-J., et al. 2013, MNRAS, 443, 1065

%\bibitem[Beutler et al.(2016)]{Beutler2016}
%Beutler, F., Seo, H.-J., \& Saito, S., et al. 2016,
%arXiv:1607.03150

\bibitem[Blake et al.(2011)]{Blake2011}
Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725

%\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
%Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488

%\bibitem[Bolton et al.(2012)]{Bolton2012}
%Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144

%\bibitem[Boylan-Kolchin et al.(2008)]{B08}
%Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93

%\bibitem[Bueno Belloso et al. (2012)]{BB2012}
%Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530
